Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-05-15 paper/ms.tex
Small changes to paper
Add MV funding
Updates from Overleaf

The bottom panel of Fig.~\ref{fig:prop} shows the torque exerted on the bar by
different components. The solid lines indicate the torque on the bar by the
dark matter halo whereas the dashed line indicates the torque on the bar by
the gas phase. In the \Nbody{} case, the halo exerts a steady negative torque on
the bar, with an average torque from $1$ to $4\,\textrm{Gyr}$ of $-58.0$ in
units of $10^{10}M_{\odot}\,(\textrm{km}/\textrm{s})^2$. The halo in the
SMUGGLE case exerts a similar negative torque on the bar in the first Gyr of
evolution, but after that the halo exerts a much smaller torque on the bar,
averaging only $-7.8$ in the same units and over the same interval. The gas in
the SMUGGLE case exerts a steady positive torque averaging $11.7$ in the same
units and over the same interval.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Drummond~B.
Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson, Kathryn~V.
Johnston, Julio~F. Navarro, Joshua~S. Speagle, David~N. Spergel, Martin~D.
Weinberg, and Yanfei Zou for helpful discussions. A.B. would like to thank
Todd Phillips for helpful discussions. Some computations in this paper were
run on the FASRC Cannon cluster supported by the FAS Division of Science
Research Computing Group at Harvard University. Resources supporting this work
were also provided by the NASA High-End Computing (HEC) Program through the
NASA Advanced Supercomputing (NAS) Division at Ames Research Center. A.B. was
supported by the Future Investigators in NASA Earth and Space Science and
Technology (FINESST) award number 80NSSC20K1536 during the completion of this
work. L.H. funding. E.D. funding. F.M. funding. C.C. funding. J.Q. funding.
L.V.S. funding. P.T. funding. M.V. funding.

@@

The time evolution of the bar strength, defined as the maximum of
$\left|A_2/A_0\right|$ as a function of radius, is shown in Extended Data
Fig.~\ref{fig:strength}. The quantity $\left|A_2/A_0\right|$ varies from $0$
to $1$, with larger values indicating a stronger bar pattern. We see that in
the \Nbody{} case, $\left|A_2/A_0\right|$ increases over time as the bar pattern
slows. This is consistent with previous \Nbody{} simulations which showed a
clear correlation between the bar pattern speed and the bar
strength.\cite{2003MNRAS.341.1179A} In the SMUGGLE case, we see that the bar
strength has an initial drop but then remains at a roughly constant but
slightly decreasing strength. This is consistent with the pattern speed in the
SMUGGLE case being roughly constant or slightly increasing.

>>>>

The bottom panel of Fig.~\ref{fig:prop} shows the torque exerted on the bar by
different components. The solid lines indicate the torque on the bar by the
dark matter halo, whereas the dashed line indicates the torque on the bar by
the gas phase. In the \Nbody{} case, the halo exerts a steady negative torque on
the bar, with an average torque from $1$ to $4\,\textrm{Gyr}$ of $-58.0$ in
units of $10^{10}M_{\odot}\,(\textrm{km}/\textrm{s})^2$. The halo in the
SMUGGLE case exerts a similar negative torque on the bar in the first Gyr of
evolution, but after that the halo exerts a much smaller torque on the bar,
averaging only $-7.8$ in the same units and over the same interval. The gas in
the SMUGGLE case exerts a steady positive torque averaging $11.7$ in the same
units and over the same interval.

@@

\item [Acknowledgements] We would like to thank Greg~L. Bryan, Neal~J. Evans,
Drummond~B. Fielding, Keith Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson,
Kathryn~V. Johnston, Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro,
Joshua~S. Speagle, David~N. Spergel, Martin~D. Weinberg, and Yanfei Zou for
helpful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. Some computations in this paper were run on the FASRC Cannon
cluster supported by the FAS Division of Science Research Computing Group at
Harvard University. Resources supporting this work were also provided by the
NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing
(NAS) Division at Ames Research Center. A.B. was supported by the Future
Investigators in NASA Earth and Space Science and Technology (FINESST) award
number 80NSSC20K1536 during the completion of this work. L.H. funding. E.D.
funding. F.M. funding. C.C. funding. J.Q. acknowledges support from NSF grant AST-2008490. L.V.S. funding. PT acknowledges support from NSF grant AST-1909933, AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges support through NASA ATP 19-ATP19-0019,
19-ATP19-0020, 19-ATP19-0167, and NSF grants AST-1814053, AST-1814259,
AST-1909831, AST-2007355 and AST-2107724.

@@

The time evolution of the bar strength, defined as the maximum of
$\left|A_2/A_0\right|$ as a function of radius, is shown in Extended Data
Fig.~\ref{fig:strength}. The quantity $\left|A_2/A_0\right|$ varies from $0$
to $1$, with larger values indicating a stronger bar pattern. We see that in
the \Nbody{} case, $\left|A_2/A_0\right|$ increases over time as the bar pattern
slows. This is consistent with previous \Nbody{} simulations which showed a
clear correlation between the bar pattern speed and the bar
strength.\cite{2003MNRAS.341.1179A} In the SMUGGLE case, we see that the bar
strength has an initial drop but then remains at a roughly constant, but
slightly decreasing, strength. This is consistent with the pattern speed in the
SMUGGLE case being roughly constant or slightly increasing.
